Black swans in ecological time series\\Black swans in population dynamics\\Heavy-tailed ecological time series

### 2014-09-30 anderson-etal-blackswan-timeseries.tex
Additions to ms

\usepackage{longtable}
\usepackage{multirow}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{tabu} % for spacing between rows in longtable
\setlength{\tabulinesep}{9pt}

@@

\section{Abstract}
- introduce black swans and heavy tails, perhaps use the climate and increasing climate variability hook

@@

Increasing realization about the importance of extreme events in the environment (REFs)
and of the importance of ecological surprises and black swans (REFs)

Papers to work in:

@@

>>>>

\usepackage{ragged2e}
\setlength\RaggedRightParindent{\parindent} % default value of this parameter is `0pt`
\RaggedRight % if invoked in preamble, entire document is set Ragged-Right

\usepackage{longtable}
\usepackage{multirow}
\usepackage{array}
\usepackage{tabu} % for spacing between rows in longtable
\setlength{\tabulinesep}{9pt}

@@

\section{Main message (25 words)}

Black swans are present, taxonomically widespread, but rare in population dynamics.
Intrinsic drivers are unclear; extreme climate, predation, parasites, and their interactions are common causes.

\section{Abstract}

- introduce black swans and heavy tails, perhaps use the climate and increasing climate variability hook

@@

\begin{enumerate}
  \item What are black swans and why do we care?

%\bigskip
\item Why might we expect to see  heavy tails in ecological timeseries?

%\bigskip
\item What is the existing evidence for heavy tails in ecological time series?

%\bigskip
\item Our research questions and main conclusions.

%Increasing realization about the importance of extreme events in the environment (REFs)
%and of the importance of ecological surprises and black swans (REFs)

\bigskip
Papers to work in:

@@

\begin{enumerate}
  \item Short overview paragraph
  \item The data: global population dynamics database
  \item The model: Gompertz population model
  \item Alternative models and sensitivity analyses
  \end{enumerate}
